Analysis Descriptives

### 2024-02-09 procesamiento/03-prod_analysis-descriptives.Rmd
up all

df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
resits_count <- df1 %>%
  group_by(country,country2) %>%
  summarise(redist = mean(redist,na.rm = T),
            egal
            homclass = mean(homclass,na.rm = T),
            pi_nteg = mean(pi_nteg,na.rm = T),
            pi_ntegm = median(pi_nteg,na.rm = T)
            ) %>%
  na.omit()

@@

df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
df2$country3 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "iso3c")
df2 <- bind_cols(df2,sjmisc::to_dummy(x = df2$class3,suffix = "numeric"))

macro_data <- df2 %>%
  group_by(country2,country3) %>%
  summarise_at(c("egal2","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
                 "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
  as.data.frame()

@@

macro_data %>%  
ggplot(aes(y=homclass, x=gini_disp)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Gini (Disposable)")+
  ylab("Class homogeneity") +
  labs(title = "Class homogeneity and Gini (Disposable)",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$gini_disp),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_giniD_homo.png",device = "png",
       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)

macro_data %>%  
ggplot(aes(y=homclass, x=gini_mkt)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Gini (Market)")+
  ylab("Class homogeneity") +
  labs(title = "Class homogeneity and Gini (Market)",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$gini_mkt),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_giniM_homo.png",device = "png",
       path = here::here("output/images"),width = 1,height = 1,units = "cm",scale = 20)

>>>>

df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
resits_count <- df1 %>%
  group_by(country,country2) %>%
  summarise(redist = mean(redist,na.rm = T),
            homclass = mean(homclass,na.rm = T),
            pi_nteg = mean(pi_nteg,na.rm = T),
            pi_ntegm = median(pi_nteg,na.rm = T)
            ) %>%
  na.omit()

@@

dfreg$country2 <- countrycode::countrycode(sourcevar = dfreg$country,origin = "iso3n",destination = "country.name")
dfreg$country3 <- countrycode::countrycode(sourcevar = dfreg$country,origin = "iso3n",destination = "iso3c")
dfreg <- bind_cols(dfreg,sjmisc::to_dummy(x = dfreg$class3,suffix = "numeric"))

macro_data <- dfreg %>%
  group_by(country2,country3) %>%
  summarise_at(c("egal2","homclass","gini_disp","gini_mkt",
                 "class3_1","class3_2","class3_3"), mean, na.rm = TRUE) %>% 
  as.data.frame()

homclass_work <- dfreg %>%
  filter(class3=="Working Class (VI+VII)") %>% 
  group_by(country3) %>%
  summarize(homclass_work= mean(homclass, na.rm = TRUE))

homclass_inte <- dfreg %>%
  filter(class3=="Intermediate class (III+IV+V)") %>% 
  group_by(country3) %>%
  summarize(homclass_inte= mean(homclass, na.rm = TRUE))

homclass_serv <- dfreg %>%
  filter(class3=="Service Class (I+II)") %>% 
  group_by(country3) %>%
  summarize(homclass_serv= mean(homclass, na.rm = TRUE))
macro_data <- 
macro_data %>% 
  full_join(homclass_work) %>% 
  full_join(homclass_inte) %>% 
  full_join(homclass_serv)

macro_data %>% 
  dplyr::select(egal2,gini_disp,starts_with("homclass"),"class3_1","class3_2","class3_3") %>% 
  correlation::correlation() %>% 
  summary()

@@

homo_ineq <- dfreg %>%
  # filter(country3 != "ZAF") %>%
  group_by(country2,country3,class3) %>%
  summarise_at(c("homclass","egal2","gini_disp","gini_mkt"), mean, na.rm = TRUE) %>% 
  as.data.frame()

homo_ineq %>%
ggplot(aes(y=homclass, x=gini_disp, group=class3,fill=class3)) +
  geom_text(label=as.character(homo_ineq$country3)) +
  geom_smooth(method = "lm",fullrange=TRUE, color="black") +
  facet_wrap(~class3) +
  xlab("Gini (Disposable)")+
  ylab("Class homogeneity") +
  labs(title = "Class homogeneity and Gini (Disposable)") +
  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C")) +
  theme(legend.position = "bottom",legend.title = element_blank())

homo_ineq %>%
ggplot(aes(y=egal2, x=homclass, group=class3,fill=class3)) +
  geom_text(label=as.character(homo_ineq$country3)) +
  geom_smooth(method = "lm",fullrange=TRUE, color="black") +
  facet_wrap(~class3) +
  xlab("Class homogeneity")+
  ylab("Redistributive preferences") +
  labs(title = "Class homogeneity and Redistributive preferences") +
  scale_fill_manual(values=c("#377EB8","#4DAF4A","#E41A1C")) +
  theme(legend.position = "bottom",legend.title = element_blank())

ggsave(plot = last_plot(),filename = "macro_giniD_homo.png",device = "png",
       path = here::here("output/images"),width = 1.5,height = 1,units = "cm",scale = 20)
